---
title: "Untitled"
author: "RQ"
date: "05/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("dplyr")
library("purrr")
```

This RMarkdown document explores the rendering of multiple dashboards.

```{r render}
rmarkdown::render(
  input = "apt_dashboard_01.Rmd"
  # , params = list(seg = "Focus1", grp = "Core", per = "Weekly")
  , output_file = "test_01.html"
  #, output_dir = "/myfiles-dir"
)
```


In order to produce a series of dashboards, the render call needs to be looped over the set of airports.
For this we 

* create an iterator, 
* pass the airport location identifier as a parameter to the template dashboard pages, and
* render the output to a specific file name (apt.html).

```{r}
apts   <- c("EGLL", "EDDF")
tfc_df <- iris

apts %>% 
  purrr::walk(
    .f=~rmarkdown::render(
      input = "apt_dashboard_03.Rmd"
      , params = list(apt = ., tfc = tfc_df)  #paste0(.))
      #, output_dir = "/boards"
      , output_file = paste0(.,"03.html")
      )
    )
```

wrap this into function and then load "payload data", filter it for apt and provide it to template with parameter
df <- readxl::read_excel(tfc, sheet = "DATA")

```{r}
apts   <- c("EGLL", "EDDF", "EIDW")


## ------------ READ DATA TABLES FROM DOWNLOAD POINT ------------------

tfc_df <- readxl::read_excel("./data-test/Airport_Traffic.xlsx", sheet = "DATA"
  # readxl style to force all chr # , col_types = "text" #
) %>%
  mutate(FLT_DATE = lubridate::date(FLT_DATE)) 

ids_df <- tfc_df %>% select(apt = APT_ICAO, name = APT_NAME, state = STATE_NAME)

thru_df <- readr::read_csv("./data-test/STAT_AIRPORT_DATA_THRU.csv") %>% rename(APT_ICAO = APT)

atfm_df <- readxl::read_excel("./data-test/Airport_Arrival_ATFM_Delay.xlsx", sheet = "DATA") %>%
  mutate(FLT_DATE = lubridate::date(FLT_DATE)) %>%
  mutate_at(vars(starts_with("DLY_APT_ARR_")), tidyr::replace_na, 0) %>%
  mutate( AD_DISRUPTION = DLY_APT_ARR_A_1 + DLY_APT_ARR_E_1 + DLY_APT_ARR_N_1 + 
            DLY_APT_ARR_O_1 + DLY_APT_ARR_NA_1
         ,AD_CAPACITY   = DLY_APT_ARR_G_1 + DLY_APT_ARR_M_1 + DLY_APT_ARR_R_1 +
           DLY_APT_ARR_V_1
         ,AD_WEATHER    = DLY_APT_ARR_D_1 + DLY_APT_ARR_W_1
         ,AD_DISRUPTION_ATC = DLY_APT_ARR_I_1 + DLY_APT_ARR_T_1
         ,AD_CAPACITY_ATC   = DLY_APT_ARR_C_1
         ,AD_STAFFING_ATC   = DLY_APT_ARR_S_1
         ,AD_EVENTS     = DLY_APT_ARR_P_1
         )

# idea was to read out the meta data to map causes to groups
#atfm_reg <- readxl::read_excel("./data-test/Airport_Arrival_ATFM_Delay.xlsx", sheet = "META"
#                               , skip = 8  # skip first rows
#                               ) %>% 
#  select(1, 4) %>%
#  filter(!is.na(`Reason Group`))

slot_df <- readxl::read_excel("./data-test/ATFM_Slot_Adherence.xlsx", sheet = "DATA")

asma_df <- readxl::read_excel("./data-test/ASMA_Additional_Time.xlsx", sheet = "DATA")

txot_df <- readxl::read_excel("./data-test/Taxi-Out_Additional_Time.xlsx", sheet = "DATA")

txit_df <- readr::read_csv("./data-test/STAT_AIRPORT_DATA_TXIT.csv") %>% rename(APT_ICAO = APT)

pddly_df<- readxl::read_excel("./data-test/STAT_AIRPORT_DATA.xlsx", sheet = "DATA") %>%
  select(APT_ICAO, APT_IATA, YEAR, MONTH_NUM, TOTAL_DLY_89, TOTAL_DLY_999, TOTAL_DLY_ZZZ
         ,TOTAL_DLY_OTHER, TOTAL_UN_RPTED_DLY, TOTAL_OV_RPTED_DLY)

turn_df <- readr::read_csv("./data-test/STAT_AIRPORT_DATA_TURN.csv") %>% rename(APT_ICAO = APT)

punc_df <-  readr::read_csv("./data-test/STAT_AIRPORT_DATA_PUNC.csv") %>% rename(APT_ICAO = APT)
```

```{r}
## ------------ UTILITY FUNCTIONS -------------------------------------

filter_df_by_apt <- function(.df, .apt){
  df <- .df %>% filter(APT_ICAO == .apt)
}

pick_apt_name <- function(.df, .apt){
  name <- .df %>% filter(APT_ICAO == .apt)
  name <- name$APT_NAME[1]
}

pick_state_name <- function(.df, .apt){
  state <- .df %>% filter(APT_ICAO == .apt)
  state <- state$STATE_NAME[1]
}

pick_apt_iata <- function(.df, .apt){
  iata <- .df %>% filter(APT_ICAO == .apt)
  iata <- iata$APT_IATA[1]
}
```

## ------------ RENDER DASHBOARDS -------------------------------------

```{r}
apts %>% 
  purrr::walk(
    .f=~rmarkdown::render(
        input  = "apt_dashboard_04.Rmd"
      , params = list( #------ start params -------------------------
           icao = .
          ,iata = pick_apt_iata( pddly_df,  .apt = .)   # merge iata code with other source 
          ,name = pick_apt_name(   tfc_df,  .apt = .)
          ,state= pick_state_name( tfc_df,  .apt = .)
          ,tfc  = filter_df_by_apt(tfc_df,  .apt = .)
          ,thru = filter_df_by_apt(thru_df, .apt = .)
          ,atfm = filter_df_by_apt(atfm_df, .apt = .)
          ,slot = filter_df_by_apt(slot_df, .apt = .)
          ,asma = filter_df_by_apt(asma_df, .apt = .)
          ,txot = filter_df_by_apt(txot_df, .apt = .)
          ,txit = filter_df_by_apt(txit_df, .apt = .)
          ,pddly= filter_df_by_apt(pddly_df,.apt = .)
          ,turn = filter_df_by_apt(turn_df, .apt = .)
          ,punc = filter_df_by_apt(punc_df, .apt = .)
          ) #----------------- end params ---------------------------
    #  , output_dir = "./boards"   # brittle as reported in stackoverflow
      , output_file = paste0("./boards/", .,"-04.html")
      )
    )
```

geht nicht mehr

apts %>% 
  purrr::walk(
    .f=~rmarkdown::render(
      #input = "apt_dashboard_01.Rmd"
      input = "apt_dashboard_02.Rmd"
      , params = list(apt = . 
                      , tfc = filter_df_by_apt(tfc_df, .apt = .)  
      ) # end params list
                      #   #paste0(.)) .. %>% filter_df_by_apt(.apt = .)   )
      #, output_dir = "/boards"
      , output_file = paste0(.,".html")
      )
    )



                   
