---
title: "Untitled"
author: "RQ"
date: "12/03/2020"
output: html_document
---

```{r setup, include=FALSE}
grp <- c("A","B","C","D")
xval <- as.factor(c("x","y","x","y"))
frame <- merge(grp, xval, all=T)
yval <- as.factor(c('low', 'low-medium', 'medim-high', 'high'))
df <- tbl_df(cbind(frame, yval))
colnames(df) <- c("category", "Type", "Range")

p <- df %>% 
  group_by(category) %>% 
  arrange(Type) %>%
  plot_ly(
    x = ~Type, 
    y = ~Range, 
    color= ~category,
    colors = 'Reds',
    type = 'bar',
    legendgroup = "A")

pp <- df %>% 
  group_by(category) %>% 
  arrange(Type) %>%
  plot_ly(
    x = ~Type, 
    y = ~Range, 
    color= ~category,
    colors = 'Reds',
    type = 'bar',
    legendgroup = "A",
    showlegend=F)


subplot(p,pp,shareY = T) %>% layout(barmode = 'stack')
```



```{r}
df = data.frame(
year = c(2014,2014,2014,2015,2015,2015,2016,2016,2016),
pet = c("dog","cat","bird","dog","cat","bird","dog","cat","bird"),
wt_before = c(56, 25, 26, 10, 19, 41, 16, 17, 13),
wt_after = c(49, 18, 19,  3, 12, 34,  9, 10,  6)
)


xaxis_length <- length(unique(df$year))
animal_no <- length(unique(df$pet))

i <- 0
for (animal in unique(df$pet)) {
  x <- seq(0, 
           animal_no  * xaxis_length + xaxis_length, 
           by = xaxis_length + 1) + i
  i <- i + 1
}
```


```{r}
for (animal in unique(df$pet)) {
  x <- seq(0, 
           animal_no  * xaxis_length + xaxis_length, 
           by = xaxis_length + 1) + i
  i <- i + 1
  p <- add_trace(p,
                 data=df[df$pet == animal, ], 
                 x = x, 
                 y = ~wt_after, 
                 type = 'bar'
                 )

  p <- add_trace(p, 
                 data=df[df$pet == animal, ], 
                 x = x,
                 y = df[df$pet == animal, ]$wt_before - df[df$pet == animal, ]$wt_after, 
                 type = 'bar'                 
  )
}
p
```

```{r}
df = data.frame(
  year = c(2014, 2014, 2014, 2015, 2015, 2015, 2016, 2016, 2016, 2017, 2017, 2017),
  pet = c("dog", "cat", "bird", "dog", "cat", "bird", "dog", "cat", "bird", "dog", "cat", "bird"),
  wt_before = c(56, 25, 26, 10, 19, 41, 16, 17, 13, 20, 25, 30),
  wt_after = c(49, 18, 19,  3, 12, 34,  9, 10,  6, 15, 20, 22)
)

colors <- c('rgba(97,156,255,', 
            'rgba(0,186,56,', 
            'rgba(248,118,109,')

xaxis_length <- length(unique(df$year))
animal_no <- length(unique(df$pet))

names(colors) <- unique(df$pet)

p <- plot_ly() %>% layout(barmode = 'stack') %>% 
  layout(barmode = 'stack', 
         xaxis=list(ticktext = unique(df$year),
                    tickvals = seq(1, 
                                   xaxis_length * animal_no +  xaxis_length, 
                                   by = xaxis_length + 1)
                    ),
         bargap=0)

i <- 0
for (animal in unique(df$pet)) {

  x <- seq(0, 
           animal_no  * xaxis_length + xaxis_length, 
           by = xaxis_length + 1) + i
  i <- i + 1
  p <- add_trace(p,
               data=df[df$pet == animal, ], 
               x = x, 
               y = ~wt_after, 
               type = 'bar', 
               name = animal,
               marker = list(color = paste(colors[[animal]], 
                                           ",1)", 
                                           sep = "")
                           ),
               legendgroup = animal,
               text = ~wt_after,
               hoverinfo = 'text'
               )

  p <- add_trace(p, 
                 data=df[df$pet == animal, ], 
                 x = x,
                 y = df[df$pet == animal, ]$wt_before - df[df$pet == animal, ]$wt_after, 
                 type = 'bar', 
                 name = animal,
                 marker=list(color = paste(colors[[animal]], 
                                           ",0.5)", 
                                           sep = "")
                             ),
                 legendgroup = animal,
                 showlegend = FALSE,
                 text = ~wt_before,
                 hoverinfo = 'text'

  )
}
p
```



```{r}
library(ggplot2)

df <- punc_df %>% filter(APT_ICAO=="EGLL", SRC_PHASE == "DEP", YEAR == max(YEAR)) %>% 
  group_by(YEAR, MONTH, GROUP) %>% 
  summarise(N_GRP_MN = sum(N_GRP)) %>% ungroup() %>% 
  mutate(SHARE = N_GRP_MN / sum(N_GRP_MN)) 

g2 <- ggplot( data    = df
             ,mapping = aes(x = MONTH, y = round(100 * SHARE, 2), fill = GROUP)) +
  geom_col(width = 0.8, position = position_fill(reverse = TRUE)) + 
  theme_minimal()

g3 <- g2 %>% hide_legend()            

subplot(style(g3, showlegend = FALSE),g2, shareY = TRUE, nrows = 1, widths = c(0.3,0.7)) %>%
  layout(legend = list(orientation = 'h', x = 0, y =-0.1))
```


```{r}
gt <- ggplot(mtcars, aes(x=wt, y=cyl, fill = factor(cyl))) + geom_col()
gt %>% hide_legend()
```
```{r}
fig <- plot_ly(
  labels = c("Eve", "Cain", "Seth", "Enos", "Noam", "Abel", "Awan", "Enoch", "Azura"),
  parents = c("", "Eve", "Eve", "Seth", "Seth", "Eve", "Eve", "Awan", "Eve"),
  values = c(10, 14, 12, 10, 2, 6, 6, 4, 4),
  type = 'sunburst'
)

fig
```

```{r}
df2 <- df %>% mutate(
  SUBGROUP = case_when(
     GROUP == "EARLY 0-5"   ~ "WI5"
    ,GROUP == "EARLY 5-15"  ~ "WI15"
    ,GROUP == "EARLY 15-30" ~ "EARLY"
    ,GROUP == "EARLY 30+"   ~ "EARLY"
    ,GROUP == "LATE 0-5"    ~ "WI5"
    ,GROUP == "LATE 5-15"   ~ "WI15"
    ,GROUP == "LATE 15-30"  ~ "LATE"
    ,GROUP == "LATE 30-60"  ~ "LATE"
    ,GROUP == "LATE 60+"    ~ "LATE"
    , TRUE ~ "NA"
  ))

fig <- plot_ly(
  labels = df2$SUBGROUP,
  parents = df2$GROUP,
  values = df2$SHARE,
  type = 'sunburst'
)

fig
```

```{r}
pd <- data.frame(
    ids = c(
    "North America", "Europe", "Australia", "North America - Football", "Soccer",
    "North America - Rugby", "Europe - Football", "Rugby",
    "Europe - American Football","Australia - Football", "Association",
    "Australian Rules", "Autstralia - American Football", "Australia - Rugby",
    "Rugby League", "Rugby Union"
  ),
  labels = c(
    "North<br>America", "Europe", "Australia", "Football", "Soccer", "Rugby",
    "Football", "Rugby", "American<br>Football", "Football", "Association",
    "Australian<br>Rules", "American<br>Football", "Rugby", "Rugby<br>League",
    "Rugby<br>Union"
  ),
  parents = c(
    "", "", "", "North America", "North America", "North America", "Europe",
    "Europe", "Europe","Australia", "Australia - Football", "Australia - Football",
    "Australia - Football", "Australia - Football", "Australia - Rugby",
    "Australia - Rugby"
  ),
  stringsAsFactors = FALSE
)

```

```{r}
#library(htmltools)
library(sunburstR)
library(d3r)

df22 <- df2 %>% group_by(SUBGROUP, GROUP) %>% 
  summarise(N = sum(N_GRP_MN)) %>%
  select(level1 = SUBGROUP, level2=GROUP, size = N)
 
dat <- data.frame(
  level1 = rep(c("a", "b"), each=3),
  level2 = paste0(rep(c("a", "b"), each=3), 1:3),
  size = c(10,5,2,3,8,6),
  stringsAsFactors = FALSE
)
#df22 <- dat

tree <- d3_nest(df22, value_cols = "size")

sb1 <- sunburst(tree, width="100%", height=400)
sb1
sb2 <- sunburst(
  tree,
  legend = FALSE,
  width = "100%",
  height = 400
)
sb2

sb3 <- sund2b(tree, width="100%")
sb3
```








atfm_pm %>% group_by(REG_REASON) %>%
  summarise( FLT_ARR_TOT = sum(FLT_ARR_TOT, na.rm = TRUE)
            ,DLY =         sum(DLY, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(DLY_TOT    = sum(DLY, na.rm = TRUE)
         ,DLY_SHARE = DLY / DLY_TOT ) %>%
  
  plot_ly(labels = ~REG_REASON, values = ~DLY_SHARE) %>%
    add_pie(hole = 0.4)


```{r}
rq <- punc_df %>% filter(APT_ICAO=="EGLL", YEAR==2019, SRC_PHASE=="DEP") %>%
mutate(
    SUBGROUP = case_when(
      GROUP == "EARLY 0-5"   ~ "WI5"
      ,GROUP == "EARLY 5-15"  ~ "WI15"
      ,GROUP == "EARLY 15-30" ~ "EARLY"
      ,GROUP == "EARLY 30+"   ~ "EARLY"
      ,GROUP == "LATE 0-5"    ~ "WI5"
      ,GROUP == "LATE 5-15"   ~ "WI15"
      ,GROUP == "LATE 15-30"  ~ "LATE"
      ,GROUP == "LATE 30-60"  ~ "LATE"
      ,GROUP == "LATE 60+"    ~ "LATE"
, TRUE ~ "NA"
)) %>% group_by(SUBGROUP, GROUP) %>%
  summarise(N = sum(N_GRP)) %>% ungroup()

tot <- tibble(GROUP = "TOTAL", N = sum(rq$N), SUBGROUP = "")

rq2 <- tot %>% bind_rows(rq)

plot_ly(
   labels = rq2$GROUP
  ,parents= rq2$SUBGROUP
  ,values = rq2$N
  ,type   = "sunburst"
)
```

GROUP            N SUBGROUP
   <chr>        <dbl> <chr>   
 1 TOTAL       200218 NA      
 2 EARLY 15-30  23010 EARLY   
 3 EARLY 30+    22903 EARLY   
 4 LATE 15-30    1024 LATE    
 5 LATE 30-60      12 LATE    
 6 LATE 60+         7 LATE    
 7 EARLY 5-15   42362 WI15    
 8 LATE 5-15    29121 WI15    
 9 EARLY 0-5    41161 WI5     
10 LATE 0-5     40618 WI5  

mylbl <- c("Punctuality","Within 15 min")
> mypar <- c("","Punctuality")
> myvals<- c(200218, 42362)
> rq <- tibble(labels = mylbl, parents = mypar, values = myvals)
> rq
# A tibble: 2 x 3
  labels        parents       values
  <chr>         <chr>          <dbl>
1 Punctuality   ""            200218
2 Within 15 min "Punctuality"  42362
> tot <- tibble(GROUP = "TOTAL", N = sum(rq$N), SUBGROUP = "")
Unknown or uninitialised column: 'N'.
> 
> rq2 <- tot %>% bind_rows(rq)
> 
> plot_ly(
+    labels = rq2$GROUP
+   ,parents= rq2$SUBGROUP
+   ,values = rq2$N
+   ,type   = "sunburst"
+ )
> plot_ly(labels = rq$labels, parents = rq$parents, values=rq$values, type = "sunburst")


```{r}
library(data.table)
library(plotly)

DF <- data.table(ownership=c(rep("private", 3), rep("public",3),rep("mixed", 3)),
                  landuse=c(rep(c("residential", "recreation", "commercial"),3)),
                  acres=c(108, 143, 102, 300, 320, 500, 37, 58, 90))

as.sunburstDF <- function(DF, valueCol = NULL){
  require(data.table)

  DT <- data.table(DF, stringsAsFactors = FALSE)
  DT[, root := "total"]
  setcolorder(DT, c("root", names(DF)))

  hierarchyList <- list()
  if(!is.null(valueCol)){setnames(DT, valueCol, "values", skip_absent=TRUE)}
  hierarchyCols <- setdiff(names(DT), "values")

  for(i in seq_along(hierarchyCols)){
    currentCols <- names(DT)[1:i]
    if(is.null(valueCol)){
      currentDT <- unique(DT[, ..currentCols][, values := .N, by = currentCols], by = currentCols)
    } else {
      currentDT <- DT[, lapply(.SD, sum, na.rm = TRUE), by=currentCols, .SDcols = "values"]
    }
    setnames(currentDT, length(currentCols), "labels")
    hierarchyList[[i]] <- currentDT
  }

  hierarchyDT <- rbindlist(hierarchyList, use.names = TRUE, fill = TRUE)

  parentCols <- setdiff(names(hierarchyDT), c("labels", "values", valueCol))
  hierarchyDT[, parents := apply(.SD, 1, function(x){fifelse(all(is.na(x)), yes = NA_character_, no = paste(x[!is.na(x)], sep = ":", collapse = " - "))}), .SDcols = parentCols]
  hierarchyDT[, ids := apply(.SD, 1, function(x){paste(x[!is.na(x)], collapse = " - ")}), .SDcols = c("parents", "labels")]
  hierarchyDT[, c(parentCols) := NULL]
  return(hierarchyDT)
}

sunburstDF <- as.sunburstDF(DF, valueCol = "acres")

plot_ly(data = sunburstDF, ids = ~ids, labels= ~labels, parents = ~parents, values= ~values, type='sunburst') #, branchvalues = 'total')
```

```{r}
asma <- asma_df %>% filter(APT_ICAO == "EGLL")

max_yr <- asma$YEAR %>% max() %>% unique
max_mn <- asma %>% 
  filter(YEAR == max(YEAR)) %>% 
  filter(MONTH_NUM == sum(!is.na(FLT_ASMA_UNIMP_2))) %>%
  pull(MONTH_NUM) %>% unique()

asma_ytd <- asma  %>% 
  filter(YEAR == max(YEAR)) %>% 
  mutate(AVG_ADD_ASMA = TIME_ASMA_ADD_2 / FLT_ASMA_UNIMP_2)
asma_ytd <- asma_ytd[1:max_mn,] %>% select(MONTH_NUM, AVG_ADD_ASMA)

rq <- sparkline(asma_ytd$AVG_ADD_ASMA, type="line")
rq
sparkline(asma_ytd$AVG_ADD_ASMA, type="bar")
sparkline(asma_ytd$AVG_ADD_ASMA, type="bullet")
```

```{r}
library(formattable)
library(sparkline)

formattable(
  data.frame(Large = LETTERS[1:4], small = letters[4:1], Rank = NA),
  list(
    "Rank"=function(z) {
      sapply(
        paste0(text='`r htmltools::tagList(sparkline(sample(5)))`')
        ,function(md) knitr::knit(text=md, quiet=T)
      )
    }
  )
)
```

```{r}
library(sparkline)
library(htmltools)
library(htmlwidgets)
library(dplyr)

mtcars %>%
  group_by(cyl) %>%
  summarise(
    hp = as.character(
      as.tags(
        sparkline(hp, type="box", chartRangeMin=0, chartRangeMax=400)
      )
    ),
    mpg = as.character(
      as.tags(
        sparkline(mpg, type="box", chartRangeMin=0, chartRangeMax=50)
      )
    )
  ) %>%
  formattable() %>%
  formattable::as.htmlwidget() %>%
  modifyList(
    list(dependencies = c(
      htmlwidgets:::getDependency("sparkline")
    ))
  )
```

```{r}
mtcars %>%
  group_by(cyl) %>%
  summarise(
    hp = as.character(
      as.tags(
        sparkline(hp, type="box", chartRangeMin=0, chartRangeMax=400)
      )
    ),
    mpg = as.character(
      as.tags(
        sparkline(
          round(density(mpg,from=0,to=tail(pretty(mtcars$mpg),1))$y,2),
          type="line"
        )
      )
    )
  ) %>%
  formattable() %>%
  formattable::as.htmlwidget() %>%
  modifyList(
    list(dependencies = c(
      htmlwidgets:::getDependency("sparkline")
    ))
  )
```















